### 2020-07-31 cases_and_policies/rmd/regressionsWithPlots.Rmd
Some simple updates.

sgtype <- opts_knit$get("rmarkdown.pandoc.to")
sgstyle <- 'default'
colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
rootdir <- "/Users/Hiro/Documents/GitHub/covid-impact" 
source(paste(rootdir,"cases_and_policies/R/exploratory.R", sep="/"))
source(paste(rootdir,"cases_and_policies/R/dataprep.R",sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/varlabels.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/regprep.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/generatetables.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/bootstrap_felm.R", sep="/"))
```

@@

<!-- ## Deaths (with cases as information) -->

<!-- ```{r deathtables, eval = FALSE, cache=FALSE, warning=FALSE, results='asis'} -->
<!-- infovars <- list(c("dlogdc", "logdc"), -->
<!--                  c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #, -->
<!-- df$zero <- 0 -->
<!-- L <- 21 -->
<!-- sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) -->
<!-- regs <- mainregressions(sdf, -->
<!--                         "dlogdd", pols, bvars, infovars, "zero", xlist, ilist, iv, L=L) -->
<!-- showhtmltables(regs$pib[[1]], regs$pbiy, regs$piy); -->
<!-- savetextables(NULL, regs$pbiy, regs$piy, prefix="deaths-casesinfo") -->
<!-- ``` -->

@@

}
showhtmltables(NULL, NULL, piy);
# savetextables(NULL, NULL,  piy, prefix="deaths-robust")

```

@@

yvar <- "dlogdc"
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national"))
tvars <- "dlogtests"  
L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
for (k in 1:length(infovars)) { 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  m$reg$beta[1:(9+2*(k-1))] <- m$bc2[1:(9+2*(k-1))] 
  #m$reg$beta[1:(6+2*(k-1))] <- m$bc[1:(6+2*(k-1))]  
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex") 
  # pols <- c("pmaskbus","pk12","pmovie","pindex") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m 
  m$reg$beta[1:(6+2*(k-1))] <- m$bc2[1:(6+2*(k-1))] 
  #m$reg$beta[1:(5+2*(k-1))] <- m$bc[1:(5+2*(k-1))] 
  piy[[(4+4*(k-1))]] <- m 
}

>>>>

sgtype <- opts_knit$get("rmarkdown.pandoc.to")
sgstyle <- 'default'
colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
source(paste(rootdir,"cases_and_policies/R/exploratory.R", sep="/"))
source(paste(rootdir,"cases_and_policies/R/dataprep.R",sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/varlabels.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/regprep.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/generatetables.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/bootstrap_felm.R", sep="/"))
```

@@

@@

}
showhtmltables(NULL, NULL, piy);
# savetextables(NULL, NULL,  piy, prefix="deaths-robust")
```

@@

yvar <- "dlogdc"
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national"))
tvars <- "dlogtests"
L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
for (k in 1:length(infovars)) {
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential")
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  #m$reg$beta[1:(9+2*(k-1))] <- m$bc2[1:(9+2*(k-1))]
  m$reg$beta <- m$bc2
  #m$reg$beta[1:(6+2*(k-1))] <- m$bc[1:(6+2*(k-1))]
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex")
  # pols <- c("pmaskbus","pk12","pmovie","pindex")
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m
  #m$reg$beta[1:(6+2*(k-1))] <- m$bc2[1:(6+2*(k-1))]
  m$reg$beta <- m$bc2
  piy[[(4+4*(k-1))]] <- m
}
